\huge Tor's Usability for Censorship Circumvention

### 2016-05-09 pets2017-paper/pets2017-paper.tex
killed some orphans and trailing words

Previous user studies have considered the whole browsing experience,
without focusing on specific features in isolation.
Our study focuses on 
the browser's configuration interface, which guides users through setting up network components required to circumvent censorship.

@@

\subsection{Tor, Tor Browser, and Tor Launcher}
The recommended way to use Tor is through Tor Browser~\cite{torbrowser},
a modified Firefox browser that includes a built-in Tor client.
Tor Browser has a software component called Tor Launcher that
starts, stops, and otherwise controls the underlying Tor processes.
Tor Launcher's graphical user interface gives access to a variety of 
sophisticated circumvention mechanisms, asking the user
to configure a proxy and bridge (if necessary) before connecting to Tor
for the first time. This is the object of our study.

@@

In addition to Tor-specific components, a proxy may be necessary to connect 
outside the local network in certain managed environments, such as corporate or university networks.
Configuring a proxy requires providing the proxy protocol, IP address, port, and additional optional
fields. There is no assistance or automation with this process. The user must locate the 
proxy information and correctly input this information into the configuration interface.

@@

\subsection{Circumventing Censorship with Tor}
There are many valid configuration settings to connect to the Tor network.
For instance, a user who does not need a bridge or proxy to circumvent censorship
can connect to Tor with a bridge and proxy, provided that they have been configured correctly. 
The minimum amount of configuration required, therefore, the set of valid configuration settings,
vary depending on the censorship environment. In the worst case, users must know or find out:\\

\begin{itemize}
	\item{Whether they are censored} 
	\item{Whether the Tor network is censored by their ISP}
	\item{Which groups of hard-coded bridges work in their environment} 
	\item{If no hard-coded bridges work, how to get and enter a custom bridge} 
	\item{Whether a proxy is required to access the Internet}
	\item{If a proxy is required, and if so, the proxy settings}
\end{itemize}

@@

An ideal interface maximizes the amount of people that successfully connect to the Tor network, while minimizing the time it takes to connect to the Tor network.

@@

\item [E3: Comprehensive censorship.]
(Representative of countries such as China and Syria.)
The E3 environment blocks websites and Tor relays like E1 and E2
and additionally blocks built-in default bridge IP addresses in the Tor Browser source code.
To succeed in this environment, participants had to select
one of the ``meek'' built-in bridges (no other type would work)
or acquire their own custom bridge and enter it manually.
\end{description}

@@

We recruited our users from Craigslist, vaguely stating that we wanted to evaluate some piece of software. 
The recruitment text can be found in Appendix~\ref{qualitative-recruitment}. The recruitment posting contained a 
SurveyGizmo online survey that collected their demographics, technical expertise, and familiarity with Tor.
The complete prescreening survey can be found in Appendix~\ref{qualitative-prescreening}.  
We selected participants in each censorship environment to have at least one person who has never heard of Tor, 
at least one person who has only heard of Tor, and exactly one person who has previously used Tor. We tried to evenly distribute any participants who had technical
expertise or used particular security tools throughout the censorship environments.

Out of our 16 participants, ages ranged from 20 to~62 years
($\mu = 24.5$, $\sigma = 12.6$). 53.3\% were male. 
93.3\% of our participants had at least
a college education.
4 participants had used Tor before;
5 had heard of Tor but had not used it;
and the remaining 8 had never heard nor used it.

@@

After participants completed the browsing tasks or ran out of time,
we interviewed them about their experience,
taking notes of the questions and answers.
We asked three standard questions asking about their general experience, 
interface features they found confusing, and feedback for improvements. We followed up
with specific questions prompted from watching their screen. 
This was to verify any hypotheses we had (e.g. ``they did not know what to do on window~3'').
We paid each participant~\$30 for their time.

@@

These changes result in a redesigned interface which we refer to as ``NEW.'' Note that the new interface preserves all the functionality of the old interface and still allows users to have control over their own network traffic.

\section{Quantitative Analyses of the Interfaces (Study 2)}
\label{sec:quantitative}
Having identified problems with the existing interface
and done a redesign in an attempt to ameliorate them,
we quantify the existing problems
and the impact of our changes with a study involving a larger number of users.
We split participants by simulated censorship environments,
and between old and new interfaces.

@@

After instructions, researchers maintained minimal interactions with the participants, 
only answering logistical questions. Participants had
about 40 minutes to complete their worksheet.
The participants did not know the details of their censorship environment,
only that they are actively being censored. Participants needed to configure Tor Browser to 
circumvent the simulated censorship.

@@

\subsection{Discussion} 
This section details general trends in user behavior, common failure cases, and our recommendations for 
improving the Tor configuration interface.

@@

\item {\bfseries Used the bridges auto-responder incorrectly (2/21).} P96, P111, who were in E3, emailed the bridges auto-responder to get custom bridges. However, they formatted the message incorrectly and thus failed to get a response. For details, see Appendix~\ref{failed-participants}.

We discarded data on participants who chose to download their own version of Tor Browser online. 5 participants downloaded their own version without trying the provided one on their desktop, while others did so after feeling frustrated with the provided version. Appendix~\ref{tor-downloads} gives the unfortunate details of where Tor was downloaded when torproject.org was blocked.
\end{description}

@@

We recommend best practices, such as providing a summary screen to let the user know the configuration settings before connecting, and having a progress bar that gives users feedback on what network component has failed.

\section{Limitations} 
The interface was only tested on Windows machines. The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems. Participants who are not accustomed to using Windows machines may have been slower to complete the given task, but this affected all conditions equally.

>>>>

Previous user studies have considered the whole browsing experience,
without focusing on specific features in isolation.
Our study focuses on 
the browser's configuration interface, which guides users through setting up components required to circumvent censorship.

@@

\subsection{Tor, Tor Browser, and Tor Launcher}
The recommended way to use Tor is through Tor Browser~\cite{torbrowser},
a modified Firefox browser that includes a built-in Tor client.
Tor Browser has a component called Tor Launcher that
starts, stops, and otherwise controls the underlying Tor processes.
Tor Launcher's graphical user interface gives access to 
sophisticated circumvention mechanisms, giving the user
the option to configure a proxy and bridge before connecting to Tor
for the first time. This is the object of our study.

@@

In addition to Tor-specific components, a proxy may be necessary to connect 
outside the local network in certain managed environments, such as corporate or university networks.
Configuring a proxy requires providing the proxy protocol, IP address, port, and additional optional
fields. There is no assistance or automation with this process. The user must locate the 
proxy information and correctly input this information.

@@

\subsection{Circumventing Censorship with Tor}
There are many valid configuration settings to connect to the Tor network.
For instance, a user who does not need a bridge or proxy 
can connect to Tor with a bridge and proxy, provided that they have been configured correctly. 
The minimum amount of configuration required, therefore, the set of valid configuration settings,
vary depending on the censorship environment. In the worst case, users must know or find out:\\

\begin{itemize}
	\item{Whether their Internet connection is censored} 
	\item{Whether the Tor network is censored by their ISP}
	\item{Which hard-coded bridges work in their country} 
	\item{If no hard-coded bridges work, how to get custom bridge information and connect to it} 
	\item{Whether a proxy is required to access the Internet}
	\item{If a proxy is required, and if so, the proxy settings}
\end{itemize}

@@

An ideal interface maximizes the amount of people that successfully connect to the Tor network, while minimizing the time it takes to connect to the Tor network. A trade-off may be required between the total amount of time it takes to connect to Tor and the amount of time users interact with the interface. For instance, a  process with a balanced amount of user input may be faster than a naive but completely automated process.

@@

\item [E3: Comprehensive censorship.]
(Representative of countries such as China and Syria.)
The E3 environment blocks websites and Tor relays like E1 and E2
and additionally blocks built-in default bridge IP addresses in the Tor Browser source code.
To succeed in this environment, participants had to select
one of the ``meek'' built-in bridges (no other type of hard-coded bridges would work)
or acquire their own custom bridge and enter it manually.
\end{description}

@@

We recruited our users from Craigslist, vaguely asking to evaluate a piece of software. 
The recruitment text can be found in Appendix~\ref{qualitative-recruitment}. The recruitment posting contained a 
SurveyGizmo online survey that collected their demographics, technical expertise, and familiarity with Tor.
The complete prescreening survey can be found in Appendix~\ref{qualitative-prescreening}.  
We selected participants in each censorship environment to have at least one person who has never heard of Tor, 
at least one person who has only heard of Tor, and exactly one person who has previously used Tor. We tried to evenly distribute any participants who had technical
expertise or used particular security tools throughout the censorship environments.

Of our 16 participants, 53.3\% were male. 
Ages ranged from 20 to~62 years
($\mu = 24.5$, $\sigma = 12.6$). 
93.3\% of our participants had at least
a college education.
4 had used Tor before;
5 had heard of Tor but not used it;
and the remaining 8 had never heard nor used it.

@@

After participants completed the browsing tasks or ran out of time,
we interviewed them about their experience and
took notes of the questions and answers.
We asked three standard questions asking about their general experience, 
interface features they found confusing, and feedback for improvements. We followed up
with specific questions prompted from watching their screen. 
This was to verify any hypotheses we had (e.g. ``they did not know what an ISP was'').
We paid each participant~\$30 for their time.

@@

These changes result in a redesigned interface which we refer to as NEW. Note that the new interface preserves all the functionality of the old interface and still allows users to have control over their own network traffic.

\section{Quantitative Analyses of the Interfaces (Study 2)}
\label{sec:quantitative}
Having identified problems with the existing interface
and made changes to ameliorate them,
we quantify the existing problems
and the impact of our changes with a study involving a larger number of users.
We split participants by simulated censorship environments,
and between old and new interfaces.

@@

After instructions, researchers maintained minimal interactions with the participants, 
only answering logistical questions.
The participants did not know the details of their censorship environment,
only that they are being censored. Participants had 40 minutes to configure Tor Browser to 
circumvent the simulated censorship and visit the blocked website.

@@

\subsection{Discussion} 
We talk about the failure cases and behavioral trends observed in our quantitative user study and recommend some changes to the Tor configuration interface based on those observations.

@@

\item {\bfseries Used the bridges auto-responder incorrectly (2/21).} P96, P111, who were in E3, emailed the bridges auto-responder to get custom bridges. However, they formatted the message incorrectly and thus failed to get a response (Appendix~\ref{failed-participants}).
\end{description}

We discarded data on participants who chose to download their own version of Tor Browser online. 5 participants downloaded their own version without trying the provided one on their desktop, while others did so after feeling frustrated with the provided version. Appendix~\ref{tor-downloads} gives the unfortunate details of where Tor was downloaded when torproject.org was blocked.

@@

Although we cannot isolate their effects on users, we also recommend notifying a users with the configured settings before connecting and having a progress bar that illustrates when network component have successfully been configured or failed.

\section{Limitations} 
The configuration interface uses the native operating system's elements and their respective styling, so an interface looks slightly different across different operating systems. We only tested interface on Windows machines, which were the machines available at Xlab. Participants who are not accustomed to using Windows machines may have been slower to complete the given task, but this affected all conditions equally.
